\bf Visual diagnostics for constrained optimisation with application to guided tours

### 2020-10-10 paper/paper.Rmd
fix pca flip sign

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      root.dir = here::here(), fig.path = here::here("figs/"), 
                      fig.align = 'center')
```

@@

```{r toy-pca-aniamted, fig.cap = "(ref:toy-pca-aniamted)"}
```

(ref:toy-pca-aniamted) A selected number of frames from the animated PCA plot. With animation, it is easier to track the progrssion from the start to finish in each algorithm.

@@

Compare to the PCA plot, the animated rotation (tour) display, in Figure \ref{toy-tour}, gives a more holistic view of the search of the optimiser and these additional information gained from the animation is cruicial. This is because in essense, PCA presents one reduced space that maximises the variance and it inherently amplifies the spread of the randomly evaluated bases in the search since they have larger variance than the bases on the interpolation path. Hence when the interest is to view the interpolation path in the space, an animated rotation display provides the view of high dimension from different angles.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      root.dir = here::here(), fig.path = here::here("figs/"), 
                      fig.align = 'center', cache = TRUE, cache.path = 'cache/')
```

@@

```{r toy-pca-animated, fig.cap = "(ref:toy-pca-animated)"}
```

(ref:toy-pca-animated) A selected number of frames from the animated PCA plot. With animation, it is easier to track the progrssion from the start to finish in each algorithm.

@@

Compare to the PCA plot, the animated rotation (tour) display, in Figure \@ref(fig:toy-tour), gives a more holistic view of the search of the optimiser and these additional information gained from the animation is cruicial. This is because in essense, PCA presents one reduced space that maximises the variance and it inherently amplifies the spread of the randomly evaluated bases in the search since they have larger variance than the bases on the interpolation path. Hence when the interest is to view the interpolation path in the space, an animated rotation display provides the view of high dimension from different angles.

### 2020-10-10 paper/paper.tex
fix pca flip sign

@@

Compare to the PCA plot, the animated rotation (tour) display, in Figure \ref{toy-tour}, gives a more holistic view of the search of the optimiser and these additional information gained from the animation is cruicial. This is because in essense, PCA presents one reduced space that maximises the variance and it inherently amplifies the spread of the randomly evaluated bases in the search since they have larger variance than the bases on the interpolation path. Hence when the interest is to view the interpolation path in the space, an animated rotation display provides the view of high dimension from different angles.

>>>>

{\centering \includegraphics{/Users/hzha400/Documents/3.PhD/research/paper-tour-vis/figs/toy-pca-animated-1}

\caption{A selected number of frames from the animated PCA plot. With animation, it is easier to track the progrssion from the start to finish in each algorithm.}\label{fig:toy-pca-animated}
\end{figure}

@@

Compare to the PCA plot, the animated rotation (tour) display, in Figure \ref{fig:toy-tour}, gives a more holistic view of the search of the optimiser and these additional information gained from the animation is cruicial. This is because in essense, PCA presents one reduced space that maximises the variance and it inherently amplifies the spread of the randomly evaluated bases in the search since they have larger variance than the bases on the interpolation path. Hence when the interest is to view the interpolation path in the space, an animated rotation display provides the view of high dimension from different angles.
